DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-02 ase2017/paper.tex
wording

The \tool can automatically synthesize stable and safe digital controllers
for intricate dynamic physical plants, represented in MATLAB as a transfer
function or a state-space equation using CEGIS.  In particular, the \tool
represents the first fully automated synthesis tool that is algorithmically
and numerically sound, considering various error sources in the
implementation of the digital control algorithm and in the computational
modeling of plant dynamics~\cite{abate2017,abatecav2017}.
%
Additionally, given the current literature in controller synthesis, there is
no other MATLAB toolbox for synthesizing stable and safe digital controllers
for physical plants, while taking into account all aspects of its digital
implementation.
%
As future work, the \tool will perform synthesis of other specifications
(e.g., performance) and be combined with DSVerifier/DSValidator
Toolboxes~\cite{issta2017,dsvalidator} to verify/validate other controller
properties.

>>>>

The \tool can automatically synthesize stable and safe digital controllers
for intricate dynamic physical plants, represented in MATLAB either as a
transfer function or a state-space equation.  The \tool is the first fully
automated synthesis tool that is algorithmically and numerically sound,
considering various error sources in the implementation of the digital
control algorithm and in the computational modeling of plant
dynamics~\cite{abate2017, abatecav2017}.
%
Additionally, given the current literature in controller synthesis, there is
no other MATLAB toolbox for synthesizing stable and safe digital controllers
for physical plants that considers all aspects of their digital
implementation.
%
As future work, the \tool will perform synthesis considering additional
requirements (e.g., performance) and will be combined with the
DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to
verify/validate further controller properties.
